---
title: "RA Bootcamp Pre Assignment"
output: html_notebook
---

This file cleans the raw data and create master dataset for analysis.
```{r}
library(dplyr)
library(tidyr)
library(readxl)
library(stringr)
```


# (a) Semester data
First, set working directory and read the raw data files
```{r}
setwd("C:/Users/somei/OneDrive - London School of Economics/Year 3/RA Bootcamp/事前課題/RawData")

sem1 <- read.csv("semester_dummy/semester_data_1.csv", skip = 1, header = TRUE)
sem2 <- read.csv("semester_dummy/semester_data_2.csv")
```
Combine the datasets
```{r}
colnames(sem2) <- colnames(sem1) # Change the column names of sem2 to those of sem1
sem <- rbind(sem1, sem2) # Combine two datasets
sem$Y <- NULL # Delete "Y" column 
```


Identify and create a row of years in which universities switched to semseter system. 
```{r}
sem <- sem %>%
  group_by(unitid) %>%
  mutate(
    sem_yr = if_else(all(semester == 1) | all(semester == 0), NA_integer_, min(year[semester == 1]))
  ) %>%
  ungroup()
```

Create a dummy variable indicating after the introduction of semseter system.
```{r}
sem <- sem %>%
  mutate(sem_dummy = ifelse(year >= sem_yr, 1, 0))
```


# (b) Gradrate data (outcome)
Read datasets and concatenate them. 
```{r}
# Initialize an empty data frame
gradrate <- data.frame()

# List all CSV files in the folder
folder_path <- "C:/Users/somei/OneDrive - London School of Economics/Year 3/RA Bootcamp/事前課題/RawData/outcome"
files <- list.files(path = folder_path, pattern = "\\.xlsx$", full.names = TRUE)

# Loop through each file and read it
for (file in files) {
  temp_data <- read_excel(file)
  gradrate <- rbind(gradrate, temp_data)
}

# Sort the combined data by unitid and year
gradrate <- gradrate %>%
  arrange(unitid, year)
```

Multiply women's graduation rate by 0.01. 
```{r}
gradrate$women_gradrate_4yr <- 0.01*(gradrate$women_gradrate_4yr)
```

Calculate men's and total graduation rates and create new columns. 
```{r}
# Change data type to numeric
gradrate$m_4yrgrads <- as.numeric(gradrate$m_4yrgrads)
gradrate$totcohortsize <- as.numeric(gradrate$totcohortsize)

# Calculate graduation rate for male and total 
gradrate$men_gradrate_4yr <- (gradrate$m_4yrgrads)/(gradrate$m_cohortsize)
gradrate$total_gradrate_4yr <- (gradrate$tot4yrgrads)/(gradrate$totcohortsize)
```

Round up the values in the new columns to 3 significant figures 
```{r}
gradrate$men_gradrate_4yr <- signif(gradrate$men_gradrate_4yr, 3)
gradrate$total_gradrate_4yr <- signif(gradrate$total_gradrate_4yr, 3) 
```

Drop observations after 2010
```{r}
gradrate <- subset(gradrate, year <= 2010)
```


# (c) Covariates data
Read the raw data 
```{r}
setwd("C:/Users/somei/OneDrive - London School of Economics/Year 3/RA Bootcamp/事前課題/RawData")
cov <- read_excel("covariates/covariates.xlsx")
```
Rename column name 
```{r}
cov <- cov %>% rename(unitid = university_id)
```

Remove 'aaaa' from 'unitid' column
```{r}
cov$unitid <- str_replace_all(cov$unitid, "aaaa", "")
```

Change the data structure to wide
```{r}
cov <- cov %>% 
  pivot_wider(names_from = category, values_from = value)
```

Keep observations between 1991 and 2010 (to match other datasets)
```{r}
cov <- subset(cov, year >= 1991 & year <= 2010)
```

Identify unit IDs that exist in gradrate dataset and keep only those in cov dataset. 
```{r}
unique_ids <- gradrate %>% distinct(unitid)

cov <- cov %>% filter(unitid %in% unique_ids$unitid)


```


# (d) Construct master data
Merge all the datasets based on unitid and year
```{r}
cov$unitid <- as.numeric(cov$unitid)
cov$year <- as.numeric(cov$year)
master_data <-  sem %>% left_join(gradrate, by = c("unitid", "year"))
master_data <- master_data %>% left_join(cov, by = c("unitid", "year"))
```

Save the datasets
```{r}
int_dir = "C:/Users/somei/OneDrive - London School of Economics/Year 3/RA Bootcamp/事前課題/IntermediateData"
cov_path <- file.path(int_dir, "clean_covariates.csv")
outcome_path <- file.path(int_dir, "clean_outcome.csv")
sem_path <- file.path(int_dir, "clean_semester_dummy.csv")
master_path <- file.path(int_dir, "master.csv")
write.csv(cov, file = cov_path, row.names = FALSE)
write.csv(gradrate, file = outcome_path, row.names = FALSE)
write.csv(sem, file = sem_path, row.names = FALSE)
write.csv(master_data, file = master_path, row.names = FALSE)
```


