---
title: "RA Bootcamp Pre Training (Analysis)"
output: html_notebook
---

In this file, I calculate descriptive statistics, plot some figures and analyse the data. 

Load libraries
```{r}
library(tidyverse)
library(tidyr)
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(stats)
options(digits = 2)
options(scipen = 999)
```


# (a) Descriptive statistics
Read the master dataset. 
```{r}
setwd("C:/Users/somei/OneDrive - London School of Economics/Year 3/RA Bootcamp/事前課題/IntermediateData")

df <- read.csv("master.csv")
```
Check the number of NA counts in each column 
```{r}
na_count <- sapply(df, function(x) sum(is.na(x)))

na_count
```

Create 'switcher' dummy
```{r}
df <- df %>%
  group_by(unitid) %>%
  mutate(
    # Check if the 'semester' variable is constant for the entire sample period
    never_switcher = ifelse(all(semester == semester[1], na.rm = TRUE), 1, 0),
    # Create the switcher variable based on the new definition
    switcher = ifelse(never_switcher == 1, 0, 1)
  ) %>%
  ungroup() %>%
  select(-never_switcher)  # Remove the temporary column if not needed
```

Calculate summary statistics for whole sample, never-switchers, and switchers.
```{r}
vars <- c("semester", "total_gradrate_4yr", "women_gradrate_4yr", "men_gradrate_4yr", "instatetuition", "costs", "faculty", "totcohortsize")
summary_all <- df %>%
  select(all_of(vars)) %>%
  summarise(across(everything(), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), n=n())

summary_never <- df %>%
  filter(switcher == 0) %>%
  select(all_of(vars)) %>%
  summarise(across(everything(), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), n=n())

summary_switcher <- df %>%
  filter(switcher == 1) %>%
  select(all_of(vars)) %>%
  summarise(across(everything(), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), n=n())

# Combine the summaries into one data frame
combined_summary <- bind_rows(
  summary_all %>% mutate(Group = "All"),
  summary_never %>% mutate(Group = "Never-Switchers"),
  summary_switcher %>% mutate(Group = "Switchers")
) %>%
  pivot_longer(-Group, names_to = "Variable", values_to = "Statistic") %>%
  pivot_wider(names_from = Group, values_from = Statistic)

View(combined_summary)
```

Create LaTeX table
```{r}
combined_summary %>%
  select(Variable, All, `Never-Switchers`, Switchers) %>%
  kable("latex", booktabs = TRUE, caption = "Summary Statistics", col.names = c("Variable", "All", "Never-Switchers", "Switchers")) %>%
  kable_styling(latex_options = "hold_position") %>%
  add_header_above(c(" " = 1, "Mean (SD)" = 3)) %>%
  save_kable("summary_stats.tex")
```

Calculate and plot the graduation rate over time
```{r}
# Calculate average graduation rate for eahc year 
gradrate_avg <- df %>%
  group_by(year) %>%
  summarise(avg_gradrate = mean(total_gradrate_4yr, na.rm = TRUE))

ggplot(gradrate_avg, aes(x = year, y = avg_gradrate)) +
  geom_line() +
  geom_point() +
  ylim(0.25, 0.45) + 
  labs(title = "Average Four-Year Graduation Rate",
       x = "Year",
       y = "Four-Year Graduation Rate") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

Do the same for fractions of schools on semester
```{r}
# Calculate average graduation rate for eahc year 
sem_avg <- df %>%
  group_by(year) %>%
  summarise(avg_sem = mean(semester, na.rm = TRUE))

ggplot(sem_avg, aes(x = year, y = avg_sem)) +
  geom_line() +
  geom_point() +
  ylim(0.8, 1) + 
  labs(title = "Share of Schools on Semester",
       x = "Year",
       y = "Share of Semester Colleges") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

Finally, define a function to generate scatter plot. 
```{r}
plot_scatter <- function(data, x_var) {
  x_var_sym <- rlang::sym(x_var)
  p <- ggplot(data, aes(x = !!x_var_sym, y = total_gradrate_4yr)) +
    geom_point(size = 0.5) +
    labs(title = paste( x_var, "vs Graduation Rate"),
         x = x_var,
         y = "Graduation Rate") +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))
  
  print(p)
}
```

Define new variables
```{r}
df$female_ratio <- (df$w_cohortsize)/(df$totcohortsize)
df$white_ratio <- (df$white_cohortsize)/(df$totcohortsize)
```


Plot 
```{r}
var_list <- c("female_ratio", "white_ratio", "instatetuition")

for (var in var_list) {
  plot_scatter(data = df, x_var = var)
}
```

# (b) Regression analysis
Estimate the following regression model using OLS
\[Y_{st} = \beta_{0} + \beta_{1} \text{After}_{st} + \varepsilon_{st}\]
```{r}
model <- lm(total_gradrate_4yr ~ sem_dummy, data = df)

# Display the summary of the model
summary(model)
```

